Busch, Khakhalin. Intrinsic temporal tuning

### 2019-02-06 main.tex
tex: refs

In contrast, \textit{within} experimental groups, cells that preferred shorter synaptic inputs in dynamic clamp tended to receive longer synaptic currents, and vice versa (F(1,145)=4.9, p=0.03). We calculated differences between the properties of each individual cell and the average for the experimental group to which it belonged, and showed these deviations from respective averages on one plot (Figure 3F). Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic inputs in dynamic clamp (adjusted r=$-$0.19, p=0.02, n=151). This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, decreasing their responses to common input patterns, and enhancing responses to unusual patterns of synaptic activation  \citep{stemmler1999information}.

>>>>

In contrast, \textit{within} experimental groups, cells that preferred shorter synaptic inputs in dynamic clamp tended to receive longer synaptic currents, and vice versa (F(1,145)=4.9, p=0.03). We calculated differences between the properties of each individual cell and the average for the experimental group to which it belonged, and showed these deviations from respective averages on one plot (Figure 3F). Cells that had shorter synaptic currents, compared to other cells in their group, tended to be selective for longer synaptic inputs in dynamic clamp (adjusted r=$-$0.19, p=0.02, n=151). This means that individual neurons tended to tune their intrinsic properties away from the typical statistics of their inputs, decreasing their responses to common input patterns, and enhancing responses to unusual patterns of synaptic activation. % \citep{stemmler1999information}.
